Benefits and risks associated with children’s and adolescents’ interactions with electronic screens: An umbrella review

### 2023-03-07 reports/manuscript.Rmd
Address some small comments

```{r, load-targets}
targets::tar_load(
  c(
    "manuscript_info", "combined_bib", "plots", "prisma", "table_desc_latex",
    "edu_certain_params", "plot_edu_certain",
    "nonedu_certain_params", "plot_nonedu_certain"
  ),
  store = here::here("_targets")
)
```

@@

For each meta-analysis, two researchers independently completed the National Health, Lung and Blood Institute’s Quality Assessment of Systematic Reviews and Meta-Analyses tool [@NHLBIQualityAssessmentSystematic2014] (see Table \@ref(tab:desctable)).
We resolved disagreements by consensus, with a third researcher employed when needed.
We did not assess risk of bias in the individual studies that were included in each meta-analysis.

@@

The most frequently reported exposures were `r manuscript_info$freq_exposures`.
Supplementary File 4 provides a list of all exposures identified.
The most frequently reported outcomes were `r manuscript_info$freq_outcomes`.
In `r manuscript_info$freq_combos$n1` cases there was only one exposure/outcome combination for an age group, with `r manuscript_info$freq_combos$n2` appearing twice, and `r manuscript_info$freq_combos$ngt2` appearing three or more times.
Full characteristics of the included studies are provided in Table \@ref(tab:desctable).
<span id ="r2_23">After removing reviews with duplicate exposure/outcome combinations, our process yielded `r manuscript_info$unique_effects` unique effect/outcome combinations contributed from `r manuscript_info$prisma$unique_reviews` reviews.</span>
These effects represent the findings of `r format(manuscript_info$effects_sum$sum_k, big.mark=",")` primary studies comprised of `r format(manuscript_info$effects_sum$sum_n, big.mark=",")` participants.

```{r desctable}
table_desc_latex %>%
  knitr::kable(
    "latex",
    caption = "Review characteristics for studies providing unique effects",
    col.names = c(
      "First Author", "Year", "Design Restrictions",
      "Regions Restrictions", "Study Range",
      "Sample Age Restrictions",
      "Outcomes Assessed", "Exposures Assessed"
    ),
    escape = FALSE,
    booktabs = TRUE,
    align = c("l", "c", "l", "l", "c", "l", "l", "l"),
    linesep = "",
    longtable = TRUE
  ) %>%
  kableExtra::row_spec(1:nrow(table_desc_latex), hline_after = TRUE) %>%
  kableExtra::row_spec(0, bold = TRUE) %>%
  kableExtra::column_spec(3:4, width = "2cm") %>%
  kableExtra::column_spec(5, width = "1.5cm") %>%
  kableExtra::column_spec(6:8, width = "3cm") %>%
  kableExtra::kable_styling(
    latex_options = c("repeat_header"),
    font_size = 5
  ) %>%
  kableExtra::landscape()
```

The quality of the included meta-analyses was mixed (see Table \@ref(tab:desctable)).
Most assessed heterogeneity `r manuscript_info$qual$low_hetero`, reported the characteristics of the included studies `r manuscript_info$qual$low_char`, and used a comprehensive and systematic search strategy `r manuscript_info$qual$low_search`.
Most reviews did not clearly report if their eligibility criteria were predefined `r manuscript_info$qual$unclear_elig`.
Many papers also did not complete dual independent screening of abstracts and full text `r manuscript_info$qual$high_dualscreen` or did not clearly report the method of screening `r manuscript_info$qual$unclear_dualscreen`.
A similar trend was observed for dual independent quality assessment `r manuscript_info$qual$dualqualstr`.
Overall, only `r manuscript_info$qual$all_low` meta-analyses were graded as low risk of bias on all criteria.

>>>>

```{r, load-targets}
targets::tar_load(
  c(
    "manuscript_info", "combined_bib", "plots", "prisma",
    "edu_certain_params", "plot_edu_certain",
    "nonedu_certain_params", "plot_nonedu_certain"
  ),
  store = here::here("_targets")
)
```

@@

For each meta-analysis, two researchers independently completed the National Health, Lung and Blood Institute’s Quality Assessment of Systematic Reviews and Meta-Analyses tool [@NHLBIQualityAssessmentSystematic2014] (see Table 1).
We resolved disagreements by consensus, with a third researcher employed when needed.
We did not assess risk of bias in the individual studies that were included in each meta-analysis.

@@

The most frequently reported exposures were `r manuscript_info$freq_exposures`.
Supplementary File 4 provides a list of all exposures identified.
The most frequently reported outcomes were `r manuscript_info$freq_outcomes`.
In `r manuscript_info$freq_combos$n1` cases there was only one exposure/outcome combination for an age group, with `r manuscript_info$freq_combos$n2` appearing twice, and `r manuscript_info$freq_combos$ngt2` appearing three or more times.
Full characteristics of the included studies are provided in Table 1.
<span id ="r2_23">After removing reviews with duplicate exposure/outcome combinations, our process yielded `r manuscript_info$unique_effects` unique effect/outcome combinations contributed from `r manuscript_info$prisma$unique_reviews` reviews.</span>
These effects represent the findings of `r format(manuscript_info$effects_sum$sum_k, big.mark=",")` primary studies comprised of `r format(manuscript_info$effects_sum$sum_n, big.mark=",")` participants.

**TABLE 1**

The quality of the included meta-analyses was mixed (see Table 1).
Most assessed heterogeneity `r manuscript_info$qual$low_hetero`, reported the characteristics of the included studies `r manuscript_info$qual$low_char`, and used a comprehensive and systematic search strategy `r manuscript_info$qual$low_search`.
Most reviews did not clearly report if their eligibility criteria were predefined `r manuscript_info$qual$unclear_elig`.
Many papers also did not complete dual independent screening of abstracts and full text `r manuscript_info$qual$high_dualscreen` or did not clearly report the method of screening `r manuscript_info$qual$unclear_dualscreen`.
A similar trend was observed for dual independent quality assessment `r manuscript_info$qual$dualqualstr`.
Overall, only `r manuscript_info$qual$all_low` meta-analyses were graded as low risk of bias on all criteria.

### 2023-03-07 reports/revision_letter.Rmd
Address some small comments

@@

\WorkInProgress
\todo{Will add to table 1}

@@

\WorkInProgress
\todo{Will add to table 1}

@@

@@

@@

@@

There were two ways that the data from the primary studies could be included in our review:
* The data were provided in the paper (i.e., in forest plots, tables, or supplementary files); or
* The authors provided the data when contacted.

@@

We did not retrive data from the primary studies when the data were not provided in the paper or by the author.
We did originally consider it, but the scope was such that it was not feasible.

@@

@@

>>>>

We apologise that the quality assessment information was not included in the original submission.
We have added this information to Table 1, along with the information about the sample characteristics requested by the reviewers.
We note that this increases the size of the table, and we have removed it from the text of the manuscript and instead included it as a seperate file.

@@

\WorkInProgress
\todo{Havea added to table 1. Should we indicate on forest plots?}

@@

Our apologies for this oversight.
We initially intended to include the quality assessment in Table 1, but felt it made the table too large and moved it to a seperate table.
It seems we inadvertently did not upload the seperate file when submitting the review.
We have now included the quality assessment in Table 1.

@@

3. While we agree that this information might be useful for some readers, we found that this made the table difficult to read.
Some reviews presented multiple effect sizes, and once the information to describe each effect was added (e.e.g., the specifc outcome, exposure, age group, and moderator), the table became overwhelming.
We have included all of this information in the supplementary file.

@@

As noted in \comment{r2_15}, this has been corrected.

@@

\WorkInProgress
\todo{I think this is misleading. It differs by field, outcome, etc.}

@@

There were two ways that the data from the primary studies could be included in our review:

* The data were provided in the paper (i.e., in forest plots, tables, or supplementary files); or
* The authors provided the data when contacted.

@@

We did not retrive data from the primary studies when the data were not provided in the paper or by contacting the author.
Our results include more than 3,000 primary studies, and even after accounting for those that provided data in the paper, it would not be feasible to extract all of the remaining data.

\todo{I kind of want to say "also those reviews are probably bad anyway, because it's not hard to put data in forest plots", but I'm not sure there's a professional way to say that.}

@@

Our apologies for this oversight.
Per our response to Reviewer 2 (\comment{r2_15}), we initially intended to include the quality assessment in Table 1.
We removed it because it made the table very large, but did not include the new file with the seperate table.
We have now included the quality assessment in Table 1.

@@

Yes, we agree that this information is important.
We have included information about the sample in Table 1.
We also note that our criteria for choosing effect sizes in the case of duplicates (i.e., taking the one with the largest N) meant that we would generally take the effect size for the 'typical' population.
More concretely: in the example cited we would typically choose the effect size of television watching on learning for the general population, rather than for those who are depressed, because the sample size would be larger for the former.

\todo{should 'clinical pops' be indicated in the forest plots?}
